---
title: "Sample homework report (STAT 420, Fall 2018)"
output:
  pdf_document: default
  # html_document: default
  # word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
options(width = 1000)
```

## Name: Shiwei Lan (shiwei@illinois.edu)
## Section: X (X=2 or 4)
## NetID: shiwei; UIN: XXXX
## Department: Statistics


## Question 1 (Proof of conditional MVN)

We are given the PDF of general MVN in the lecture note 1

$$\frac{1}{(2\pi)^{p/2} \lvert \boldsymbol\Sigma \rvert^{1/2}} \exp\left\{ - \frac{1}{2} ({\bf x} - \boldsymbol\mu)^{\mathsf T} \boldsymbol\Sigma^{-1} ({\bf x} - \boldsymbol\mu) \right\}$$

Nowe we need to make use of the conditional PDF of $f(x|y)$ and try to identify it as PDF of MVN with $\mu_*$ and $\Sigma_*$ specified in the given formula. In the process you will need the following block inverse formula

\begin{equation*}
\begin{bmatrix}
\boldsymbol\Sigma_{xx} & \boldsymbol\Sigma_{xy} \\
 \boldsymbol\Sigma_{yx} & \boldsymbol\Sigma_{yy}
 \end{bmatrix}^{-1} = 
 \begin{bmatrix}
 (\boldsymbol\Sigma_{xx} - \boldsymbol\Sigma_{xy} \boldsymbol\Sigma_{yy}^{-1} \boldsymbol\Sigma_{yx})^{-1} & -(\boldsymbol\Sigma_{xx} - \boldsymbol\Sigma_{xy} \boldsymbol\Sigma_{yy}^{-1} \boldsymbol\Sigma_{yx})^{-1} \boldsymbol\Sigma_{xy} \boldsymbol\Sigma_{yy}^{-1} \\
- \boldsymbol\Sigma_{yy}^{-1} \boldsymbol\Sigma_{yx} (\boldsymbol\Sigma_{xx} - \boldsymbol\Sigma_{xy} \boldsymbol\Sigma_{yy}^{-1} \boldsymbol\Sigma_{yx})^{-1} & (\boldsymbol\Sigma_{yy} - \boldsymbol\Sigma_{yx} \boldsymbol\Sigma_{xx}^{-1} \boldsymbol\Sigma_{xy})^{-1}
 \end{bmatrix}
\end{equation*}

Look for \href{https://wch.github.io/latexsheet/latexsheet.pdf}{\underline{Latex Cheatsheet}} or other online tutorial for more details on \href{http://www.tug.org/mactex/}{\LaTeX}!


## Question 2 (see example of the MVN in the lecture notes)

We first specify the mean $\mu$ and varaince $\Sigma$ of $X$ in R:

```{r}
mu = matrix(c(5, 3, 7))
Sigma = matrix(c(4, -1, 0, -1, 4, 2, 0, 2, 9), 3, 3)
A = matrix(c(4, -3, 5))
```

We know that linear combinations of $X$ also follow the MVN distribution, and we can calculate its mean and variance by 

```{r}
Mean.AX = t(A) %*% mu
Var.AX = t(A) %*% Sigma %*% A
```

Based on this distribution, we can calculate the probablity 

```{r}
pnorm(63, mean = Mean.AX, sd = sqrt(Var.AX))
```
Hence the proabality $P(4 X_1 - 3X_2 + 5X_3 < 63) = 0.8413447$

## Question 3 (let's do a plot)

We first load the package and the dataset 

```{r}
data(mtcars)
```

We first produce a simple plot, and add a line to it
```{r fig.height = 4, fig.width = 5}
plot(mpg ~ wt, data= mtcars)
abline(lm(mpg ~ wt, data= mtcars))
```

Produce a histgram of the outcome variable, what does ``breaks'' do?

```{r fig.height = 4, fig.width = 5}
hist(mtcars$qsec, breaks = 15)
```

```{r}
x = c(2.2, 7, 4, -6)
mean(x)
# knitr::include_graphics()
```

The mean of $x$ is `r mean(x)`.
\newpage
$x_1$ and $x^2$.

[\underline{RStudio webpage}](https://www.rstudio.com)

<!-- ![caption](path/to/your/image) -->

<!-- \begin{figure} -->
<!-- \centering -->
<!-- \includegraphics[width=1\textwidth,height=0.5\textwidth]{path/to/your/image} -->
<!-- \end{figure} -->

${24 \over 3} = 8=\frac{24}{3}$

$\alpha, \beta, \beta_0, \epsilon, \varepsilon, \phi, \varphi, \chi^2_d$